Prefetching SPARQL query cacher

### 2016-07-29 dissertation/cache-proxy.tex
somewhat sloppy for more bgps

Then, to make local joins somewhat more expensive than similar BGPs\todo{check},
for both these join types, we designate the cost of joins to be
\begin{equation}\label{eq:cjoins}
C_{A \bowtie_* B} = \floor{ 1.2 n_{rs} T_{A \bowtie_{*} B} } ,
\end{equation}
where the asterisk denotes either $nl$ for nested loop or $h$ for hash
join, respectively, and $n_{rs}$ is the number of remote SPARQL Basic
Graph Patterns in the tree.

>>>>

Then, to ensure that the join rotation and coalescing can be
efficient, we penalise plans that have more of them, so
for both these join types, we designate the cost of joins to be
\begin{equation}\label{eq:cjoins}
C_{A \bowtie_* B} = \floor{ 1.2 n_{rs} T_{A \bowtie_{*} B} } ,
\end{equation}
where the asterisk denotes either $nl$ for nested loop or $h$ for hash
join, respectively, and $n_{rs}$ is the number of remote SPARQL Basic
Graph Patterns in the tree.
